\TitlePt

### 2016-03-17 conclusion.tex
Cite papers that used fatiando

\textit{Fatiando a Terra} is a library implemented in the Python programming
language.
The library contains functions and classes for data processing, visualization,
forward modeling, and inversion.
The tools for inverse problems provide generic optimization and regularization
routines that can be combined with the existing forward modeling routines to
implement new inversion methods.
To date, the project has received contributions from nine developers in three
different countries.

>>>>

\textit{Fatiando a Terra} is a library implemented in the Python programming
language.
The library contains functions and classes for data processing, visualization,
forward modeling, and inversion.
A new inversion method can be implemented by combining the existing forward
modeling functions with the problem agnostic optimization and regularization
tools in the library.
Using these tools, the amount of code required to implement new methods is
reduced, increasing the speed of the cycle of prototyping a new algorithm,
testing, and then refining it.
The project has been used in scholarly works such as
\citet{hidalgo-gato2015a}, \citet{niccoli2015}, \citet{oliveirajr.2015},
and \citet{bassett2016}.
To date, the project has received contributions from nine developers in three
different countries.
